Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2018-07-26 ms.tex

\begin{abstract}
%
%
% NOTE: Overleaf includes abstract words in word count in text... subtract
%       this from the total.
%
%
Effective stellar feedback is used in models of galaxy formation to regulate star formation and to drive realistic galaxy evolution. Energy injection from supernovae is used as the dominant form of stellar feedback, albeit often in some form of sub-grid recipe. However, it has been recently suggested that pre-SN feedback, from either stellar winds or stellar radiation, is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium. As following stellar winds and ionizing radiation is computationally challenging, many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars. In this work we use high resolution simulations of an isolated dwarf galaxy with detailed stellar feedback physics tracked on a star-by-star basis. By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test the importance of stellar ionizing radiation in regulating star formation and driving outflows in this galaxy. We find that including ionizing radiation reduces the star formation rate by over a factor of 5, and is a necessary component to drive outflows in our galaxy. In addition, we find that a localized approximation for radiation feedback is sufficient to reduce the star formation rate but, importantly does not drive significant outflows. Short and long range radiation effects are both important in driving the evolution of our modeled galaxy.
\end{abstract}

>>>>

\begin{abstract}
%
%
% NOTE: Overleaf includes abstract words in word count in text... subtract
%       this from the total.
%
%
Effective stellar feedback is used in models of galaxy formation to regulate star formation and to drive realistic galaxy evolution. Energy injection from supernovae is used as the dominant form of stellar feedback, albeit often in some form of sub-grid recipe. However, it has been recently suggested that pre-SN feedback, from either stellar winds or stellar radiation, is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM). As following stellar winds and ionizing radiation is computationally challenging, many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation. In this work we use high resolution simulations of an isolated dwarf galaxy with detailed stellar feedback physics tracked on a star-by-star basis. By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test the importance of stellar ionizing radiation in regulating star formation and driving outflows in this galaxy. We find that including ionizing radiation reduces the star formation rate by over a factor of 5, and is necessary in creating the ISM conditions needed for supernovae to drive significant outflows. In addition, we find that a localized approximation for radiation feedback is sufficient to regulate the star formation rate on short time scales, but is unable to drive the same outflows as in our fiducial model. Short and long range radiation effects are both important in driving the evolution of our modeled galaxy.
\end{abstract}
